### 2021-10-06 letter/letter.Rmd
add reviewer

\begin{itemize}
    \item Claudio Ferraz. Professor of Economics at the Vancouver School of Economics, University of British Columbia. Email: \url{claudio.ferraz@ubc.ca}.
    \item Thomas Fujiwara. Associate Professor of Economics and International Affairs, Princeton University. Email: \url{fujiwara@princeton.edu}
    \item F. Daniel Hidalgo. Cecil and Ida Green Associate Professor of Political Science, Massachusetts Institute of Technology. Email: \url{dhidalgo@mit.edu}.
    \item Guillermo Toral. Assistant Professor of Political Science, Vanderbilt University. Email: \url{guillermo.toral@vanderbilt.edu}.
\end{itemize}

To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise. All of them have written extensively about public service provision and government accountability in Brazil using modern causal inference methods.

>>>>

\begin{itemize}
    \item Claudio Ferraz. Professor of Economics at the Vancouver School of Economics, University of British Columbia. Email: \url{claudio.ferraz@ubc.ca}.
    \item Thomas Fujiwara. Associate Professor of Economics and International Affairs, Princeton University. Email: \url{fujiwara@princeton.edu}
    \item F. Daniel Hidalgo. Cecil and Ida Green Associate Professor of Political Science, Massachusetts Institute of Technology. Email: \url{dhidalgo@mit.edu}.
    \item Guillermo Toral. Assistant Professor of Political Science, Vanderbilt University. Email: \url{guillermo.toral@vanderbilt.edu}.
    \item Ryan Hübert. Assistant Professor of Political Science, University of California, Davis. Email: \url{rhubert@ucdavis.edu}.
\end{itemize}

To the best of our knowledge, none of the above-suggested persons have any conflict of interest, financial or otherwise. All of them have written extensively about public service delivery, government accountability, and economic policy analysis using modern causal inference methods.
